---
title: "Data types in R"
author: "Colin Rundel"
date: "2019-01-17"
output:
  xaringan::moon_reader:
    css: "slides.css"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
exclude: true

```{r, message=FALSE, warning=FALSE, include=FALSE}
options(
  htmltools.dir.version = FALSE, # for blogdown
  width=80
)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```



---
class: middle
count: false

# Generic Vectors


---

## Lists

Lists are _generic vectors_, in that they are 1 dimensional (i.e. have a length) and can contain any type of R object.

```{r}
list("A", c(TRUE,FALSE), (1:4)/2, function(x) x^2)
```


---

## Structure

Often we want a more compact representation of a complex object, the `str` function is useful for this particular task

```{r}
str( list("A", c(TRUE,FALSE), (1:4)/2, function(x) x^2) )
```


---

## Recursive lists

Lists can contain other lists, meaning they don't have to be flat

```{r}
str( list(1, list(2, list(3, 4), 5)) )
```


---

## List Coercion

By default a vector will be coerced to a list (as a list is more generic) if needed

```{r}
str( c(1, list(4, list(6, 7))) )
```

--

We can coerce a list into an atomic vector using `unlist` - the usual type coercion rules then apply to determine its type.

```{r}
unlist(list(1:3, list(4:5, 6)))
unlist( list(1, list(2, list(3, "Hello"))) )
```


---

## Named lists

Because of their more complex structure we often want to name the elements of a list (we can also do this with vectors). This can make reading and accessing the list more straight forward.

```{r}
str(list(A = 1, B = list(C = 2, D = 3)))
list("knock knock" = "who's there?")
names(list(ABC=1, DEF=list(H=2, I=3)))
```


---

## Exercise 2

Represent the following JSON data as a list in R.

```json
{
  "firstName": "John",
  "lastName": "Smith",
  "age": 25,
  "address": 
  {
    "streetAddress": "21 2nd Street",
    "city": "New York",
    "state": "NY",
    "postalCode": 10021
  },
  "phoneNumber": 
  [
    {
      "type": "home",
      "number": "212 555-1239"
    },
    {
      "type": "fax",
      "number": "646 555-4567"
    }
  ]
}
```

---

# Acknowledgments
## Acknowledgments

Above materials are derived in part from the following sources:

* Hadley Wickham - [Advanced R](http://adv-r.had.co.nz/)
* [R Language Definition](http://stat.ethz.ch/R-manual/R-devel/doc/manual/R-lang.html)
